---
title: "Lab 4 Report"
author: "Haider Ali"
date: "Feb-15-2021 "
output: github_document
---

```{r}

# load packages -----------------------------------------------------------
library(tidyverse)
library(auk)

# birds -------------------------------------------------------------------

birds <-                              # create a new table named birds
  ebird_taxonomy %>%                  # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
birds
```



# 1.Print a table containing only species NOT in the Order Passeriformes. Include all columns.

```{r}
filter(birds, !(order == "Passeriformes")) 
```

# 2.Print a table containing only species in the Order Passeriformes. Include all columns.
```{r}
filter(birds, (order == "Passeriformes")) 

```

# 3.Print a table containing all species. Only the variables Species Code, Scientific Name, and Common Name should be in the final table.
```{r}
select(birds,species_code , scientific_name, common_name) 
```


# 4.Print a table with all species in the Order Passeriformes whose common name starts with the word “Common”. Species should be in reverse taxonomic order (taxon_order variable). Only the variables Species Code, Scientific Name, and Common Name should be in the final table.
```{r}
big_birds <- filter(birds, (order == "Passeriformes")) 
hello <- filter(big_birds, str_detect(common_name, "Common"))
reverse <- arrange(hello,desc(taxon_order))
select(reverse,species_code:common_name)
```


# 5.Print a table containing species with “Warbler” in the common name. Include all columns.

```{r}
warbler <- filter(birds, str_detect(common_name, "Warbler"))
warbler
```

# 6.Using the species found in the previous step (with “Warbler” in their name), print a frequency table for the family variable. You should end up with a table with two columns: family and n.
```{r}
count(warbler, family)
```


# 7.print a table with all species whose common name contains a color.
```{r}
filter(birds, str_detect(common_name, "White|Black|Pink|Yellow|Blue|Green|Red|Orange|Brown|Golden"))
```


sessioninfo::session_info()










